SMT-Boosted Security Types for Low-Level MPC

### 2025-11-24 toplas26/sty.tex
checkpoint

In addition to typing judgements, in order to show that a protocol is
secure, we need to classify all corrupt views as shares, all
public values as secure openings, and all outputs as reconstructed
shares by adding them to $\Gamma$. We capture this formally with the following notion of
type environment closure.
\begin{definition}
  \label{def-sty-closed}
  $\Gamma$ is \emph{closed for $\prog$} iff for all $H,C$,
  for all $x \in \houtputs$ there exists $\phi$ such that either
  $([x,\phi] : \sharety) \in \Gamma$ if $C = \setit{1}$
  or  $([\phi,x] : \sharety) \in \Gamma$ if $C = \setit{2}$,
  and for all $\out{\cid} \in O$ we have $(\pubx{\out{\cid}} : \outty) \in \Gamma$.
\end{definition}
Now, the following is a consequence of Definitions \ref{def-OK} and \ref{def-sty-closed}, and then
our main Theorem \ref{theorem-sty} follows by Lemma \ref{lemma-OK} and Theorem \ref{theorem-OK}.
\begin{theorem}
  \label{theorem-OK}
  If $\prog,\Gamma,R : {OK}$ and $\Gamma$ is closed
  for $\prog$, then $\prog$ satisfies noninterference modulo output. 
\end{theorem}
\begin{proof}
  Let $\iov(\prog) = S \cup V \cup O$ and assume some partitioning $H,C$
  with $H = \setit{b}$ and $C = \setit{a}$ for $a,b \in \setit{1,2}$.
  %For any $\out{\cid} \in O$ with $\Gamma,\toeq{\prog} \vdash \pubx{\out{\cid}} : \outty$
  %we can assume wlog that $(\out{\cid} : \outty) \in \Gamma$, since we can
  %add the binding to $\Gamma'$ with  $\prog,\Gamma',R  : {OK}$ by Lemma
  %\ref{lemma-OK}.
  Let $\Phi_a$ and $\Phi^o$ be as defined in Definition \ref{def-OK}. 
  By Definitions \ref{def-sty-closed} we have that $x \in \houtputs$
  implies $x \in \Phi_a$ and $(\out{\cid} : \outty) \in \Gamma$ for all
  $\out{\cid} \in O$. 
  Therefore by Definition \ref{def-OK} (and marginalizing away
  extraneous $(\stt : \sty) \in \Gamma$) we have:
  $$
  \condd{\progd(\prog)}{S_H}{S_C \cup O} = \condd{\progd(\prog)}{S_H}{S_C \cup V_C \cup \Phi^p \cup O}
  $$
  By definition of $\TirName{Output}$ it is also the case that for all
  $\out{\cid} \in O$ we have $\toeq{\prog} \models o = \phi$ for some
  $\phi \in \Phi^o$. Therefore we have:
  $$
  \condd{\progd(\prog)}{S_H}{S_C \cup O} = \condd{\progd(\prog)}{S_H}{S_C \cup V_C \cup O}
  $$
  which is noninterference modulo output by Definition \ref{definition-NIMO}.
\end{proof}

>>>>

In addition to typing judgements, in order to show that a protocol is
secure, we need to classify all corrupt views as shares, all
public values as secure openings, and all outputs as reconstructed
shares by adding them to $\Gamma$. We capture this formally with the following notion of
type environment closure.
\begin{definition}
  \label{def-sty-closed}
  $\Gamma$ is \emph{closed for $\prog$} iff for all $H,C$,
  for all $x \in \houtputs$ there exists $\phi$ such that either
  $([x,\phi] : \sharety) \in \Gamma$ if $C = \setit{1}$
  or  $([\phi,x] : \sharety) \in \Gamma$ if $C = \setit{2}$,
  and for all $\out{\cid} \in O$ we have $(\pubx{\out{\cid}} : \outty) \in \Gamma$.
\end{definition}
Now, the following is a consequence of Definitions \ref{def-OK} and \ref{def-sty-closed}, and then
our main Theorem \ref{theorem-sty} follows by Lemma \ref{lemma-OK} and Theorem \ref{theorem-OK}.
\begin{theorem}
  \label{theorem-OK}
  If $\prog,\Gamma,R : {OK}$ and $\Gamma$ is closed
  for $\prog$, then $\prog$ satisfies noninterference modulo output. 
\end{theorem}
\begin{proof}
  Let $\iov(\prog) = S \cup V \cup O$ and assume some partitioning $H,C$
  with $H = \setit{b}$ and $C = \setit{a}$ for $a,b \in \setit{1,2}$.
  %For any $\out{\cid} \in O$ with $\Gamma,\toeq{\prog} \vdash \pubx{\out{\cid}} : \outty$
  %we can assume wlog that $(\out{\cid} : \outty) \in \Gamma$, since we can
  %add the binding to $\Gamma'$ with  $\prog,\Gamma',R  : {OK}$ by Lemma
  %\ref{lemma-OK}.
  Let $\Phi_a$ and $\Phi^o$ be as defined in Definition \ref{def-OK}. 
  By Definition \ref{def-sty-closed} we have that $x \in \houtputs$
  implies $x \in \Phi_a$ and $(\out{\cid} : \outty) \in \Gamma$ for all
  $\out{\cid} \in O$. 
  Therefore by Definition \ref{def-OK} (and marginalizing away
  extraneous $(\stt : \sty) \in \Gamma$) we have:
  $$
  \condd{\progd(\prog)}{S_H}{S_C \cup O} = \condd{\progd(\prog)}{S_H}{S_C \cup \houtputs \cup \Phi^p \cup O}
  $$
  By definition of $\TirName{Output}$ it is also the case that for all
  $\out{\cid} \in O$ we have $\toeq{\prog} \models o = \phi$ for some
  $\phi \in \Phi^o$. Therefore we have:
  $$
  \condd{\progd(\prog)}{S_H}{S_C \cup O} = \condd{\progd(\prog)}{S_H}{S_C \cup \houtputs \cup O}
  $$
  which is noninterference modulo output by Definition \ref{definition-NIMO}.
\end{proof}
